Geometric variational problems

### 2020-11-11 NSF2020/Description/specificaim1_ver2.tex
yny

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is characterize the material properties of many-body, self-assembled amphiphiles.
For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
Our goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
to model bilayers with specific composition. These calculations have provably less computational complexity than
those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.

@@

\subsubsection{New mathematical analysis}

We will develop some of the mathematical connections between the HAP energy and the energy functional used in the phase field method. 
The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
to the characteristic function of a set solving a perimeter minimization problem 
\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, }. 
Analogously, the HAP energy converges to the surface energy in the limit
$\rho \to 0$, and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
area measures supported on the particle boundaries. We will use boundary layer analysis to study the rate
of convergence as it depends on \cite{Stephan Luckhaus & Luciano Modica, LeeRyham}

 It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
 whether \eqref{ansatz3} contains a complete list of consistent deformations.
\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
  \textbf{(ii)}
  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
  Later, \cite{C9SM02079A} 
  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
  from a transversal tilt invariance assumption.
  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
  \textbf{(iii)}
  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
suggesting a somewhat smaller magnitude for $\KG$.

@@

  We will revisit the HK analysis to see if any of the afore mentioned inconsitencies can be resolved.
  As a main analytical innovation, we have found that expanding the strain tensor in
  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
  incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.

>>>>

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is to characterize the material properties of many-body, self-assembled amphiphiles.
For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
Our goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
to model bilayers with specific composition. These calculations have provably less computational complexity than
those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.

@@

\subsubsection{New mathematical analysis}
 It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
 whether \eqref{ansatz3} contains a complete list of consistent deformations.
\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
  \textbf{(ii)}
  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
  Later, \cite{C9SM02079A} 
  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
  from a transversal tilt invariance assumption.
  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
  \textbf{(iii)}
  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
suggesting a somewhat smaller magnitude for $\KG$.

@@

  We will revisit the HK analysis to see if any inconsitencies can be resolved.
  As a main analytical innovation, we have found that expanding the strain tensor in
  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
  incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
